\textbf{Microbiota predict \emph{Clostridium difficile} severity in germ-free mice colonized with human feces}

### 2022-01-24 submission/manuscript.Rmd
add ILB feedback

**Histopathology evaluation.** Mouse cecal tissue was placed in histopathology cassettes and fixed in 10% formalin, then stored in 70% ethanol. McClinchey Histology Labs, Inc. (Stockbridge, MI) embedded the samples in paraffin, sectioned, and created the hematoxylin and eosin-stained slides. The slides were scored using previously described criteria by a board-certified veterinary pathologist scored who was blinded to the experimental groups [@Theriot2011].

>>>>

**Histopathology evaluation.** Mouse cecal tissue was placed in histopathology cassettes and fixed in 10% formalin, then stored in 70% ethanol. McClinchey Histology Labs, Inc. (Stockbridge, MI) embedded the samples in paraffin, sectioned, and created the hematoxylin and eosin-stained slides. The slides were scored using previously described criteria by a board-certified veterinary pathologist who was blinded to the experimental groups [@Theriot2011]. Slides were scored as 0-4 for parameters of epithelial damage, tissue edema, and inflammation and a summary score of 0-12 was generated by summing the three individual parameter scores.

### 2022-01-24 submission/manuscript.tex
add ILB feedback

\textbf{Histopathology evaluation.} Mouse cecal tissue was placed in
histopathology cassettes and fixed in 10\% formalin, then stored in 70\%
ethanol. McClinchey Histology Labs, Inc.~(Stockbridge, MI) embedded the
samples in paraffin, sectioned, and created the hematoxylin and
eosin-stained slides. The slides were scored using previously described
criteria by a board-certified veterinary pathologist scored who was
blinded to the experimental groups (29).

>>>>

\textbf{Histopathology evaluation.} Mouse cecal tissue was placed in
histopathology cassettes and fixed in 10\% formalin, then stored in 70\%
ethanol. McClinchey Histology Labs, Inc.~(Stockbridge, MI) embedded the
samples in paraffin, sectioned, and created the hematoxylin and
eosin-stained slides. The slides were scored using previously described
criteria by a board-certified veterinary pathologist who was blinded to
the experimental groups (29). Slides were scored as 0-4 for parameters
of epithelial damage, tissue edema, and inflammation and a summary score
of 0-12 was generated by summing the three individual parameter scores.
